The Midplane is Not a Plane: Implications for {\em Gaia}

### 2019-03-25 paper/ms.tex
Change title
Add info about Sag sim

\shortauthors{Beane et al.}
\shorttitle{Our Galactic Midplane}

@@

\title{Issues with Dynamical Measurements Across the Disk}

@@

>>>>

\shortauthors{Beane et al.}
\shorttitle{The Midplane is Not a Plane}

@@

\title{The Midplane is Not a Plane: Implications for {\em Gaia}}

@@

\subsection{Description of Sagittarius Simulaton} \label{ssec:sag_sim}
In addition to the cosmological zoom-in, we will also briefly consider results
from a toy Sagittarius encounter simulation. This simulation offers us the
ability to see how the midplane varies in a more controlled environment. The
details of the simulation are given in \citet{2018MNRAS.481..286L}, but we
briefly summarize the most relevant details here. For the Milky Way, the dark
halo is modelled as a Hernquist sphere of mass $10^{12}\,\Msun$ and scale
length of $52\,\kpc$, the disk modelled as an exponential disk with a scale
radius of $3.5\,\kpc$, scale height $0.53\,\kpc$, and mass
$6\times10^{10}\Msun$, a Hernquist bulge of mass $10^{10}\,\Msun$ and scale
length $0.7\,\kpc$ \citep{1990ApJ...356..359H}. Sagittarius is modelled as a
dark matter Hernquist sphere of mass \Gus{something} and scale length
\Gus{something}, along with a stellar component modelled as a Hernquist sphere
of mass $6.4\times10^8\,\Msun$ and scale radius $0.85\,\kpc$.

For the disk and bulge components, a softening length of $30\,\pc$ is used
whereas for the halo a softening length of $60\,\pc$ is used. For Sagittarius,
the softening length for the dark matter and the stars is $60$ and $40\,\pc$,
respectively.
